MultiDataGrowthAssessPico

### 2023-12-15 Code/MultiDataGrowthAssessPico.Rmd
Changed save rds. to compressed "xz" to compress

saveRDS(object = NestedFitsData, file = file.path(DataOut, paste(Project, "NestedFitsData.Rds",  sep = "_")), ascii = FALSE, version = NULL, compress = TRUE, refhook = NULL)

>>>>

saveRDS(object = NestedFitsData, file = file.path(DataOut, paste(Project, "NestedFitsData.Rds",  sep = "_")), ascii = FALSE, version = NULL, compress = "xz", refhook = NULL)
